Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-09-25 main_wo_fig_tbl.Rmd
delete without figure version

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.path = "figure/",
  fig.align = "center",
  fig.show = "hold",
  cache = FALSE,
  cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
```

@@

\begin{table}[ht]
\begin{center}
\begin{tabular}{lll}
\toprule
Circular granularity & Expression & Period \\
\midrule
minute-of-hour                               &
  $C_1 = z \mod 60$                     &
  $P_1 = \phantom{99}60$ \\
minute-of-day                                &
  $C_j = z \mod 60*24$                  &
  $P_2= `r 60*24`$\\
hour-of-day                                  &
  $C_3 = \lfloor z/60\rfloor\mod 24$    &
  $P_3 = \phantom{99}24$ \\
hour-of-week                                 &
  $C_4 = \lfloor z/60\rfloor\mod 24*7$  &
  $P_4= \phantom{9}`r 24*7`$\\
day-of-week                                  &
  $C_5 = \lfloor z/24*60\rfloor \mod 7$ &
  $P_5= \phantom{999}7$\\
\bottomrule
\end{tabular}
\end{center}
\caption{Examples of circular granularities with bottom granularity minutes. Circular granularity $C_i$ relates two linear granularities one of which groups periodically into the other with regular mapping and period $P_i$. Circular granularities can be expressed using modular arithmetic due to their regular mapping. }
\label{tab:definitions}
\end{table}

@@

\begin{table}[ht]
\centering
\begin{tabular}{lr@{~}lr@{~}r}
\toprule
Quasi-circular granularity && Possible period lengths\\
\midrule
$Q_1 =$ day-of-month && $P_1 = 31, 30, 29, 28$\\
$Q_2 =$ hour-of-month && $P_2 = 24\times 31, 24\times 30, 24\times 29, 24\times 28$\\
$Q_3 =$ day-of-year && $P_3 = 366, 365$\\
$Q_4 =$ week-of-month && $P_4 = 5, 4$\\
\bottomrule
\end{tabular}
\caption{Examples of quasi-circular granularities relating two linear granularities with irregular mapping leading to several possible period lengths.}
\label{tab:quasi}
\end{table}

@@

\autoref{fig:allFig}a shows the distribution of half-hourly electricity consumption through letter value plots across months of the year faceted by quarters of the year. This plot does not work because quarter-of-the-year clashes with month-of-the-year, leading to empty subsets. For example, the first quarter never corresponds to December.

@@

For example, \autoref{fig:allFig}b shows the letter value plot across weekday/weekend faceted by quarters of the year and \autoref{fig:allFig}c shows the same two cyclic granularities with their mapping reversed. \autoref{fig:allFig}b helps us to compare weekday and weekend within each quarter and \autoref{fig:allFig}c helps to compare quarters within weekend and weekday.

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  eval = FALSE,
  comment = "#>",
  fig.path = "figure/",
  fig.align = "center",
  fig.show = "hold",
  cache = TRUE,
  cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
```

@@

<!-- \begin{table}[ht] -->
<!-- \begin{center} -->
<!-- \begin{tabular}{lll} -->
<!-- \toprule -->
<!-- Circular granularity & Expression & Period \\ -->
<!-- \midrule -->
<!-- minute-of-hour                               & -->
<!--   $C_1 = z \mod 60$                     & -->
<!--   $P_1 = \phantom{99}60$ \\ -->
<!-- minute-of-day                                & -->
<!--   $C_j = z \mod 60*24$                  & -->
<!--   $P_2= `r 60*24`$\\ -->
<!-- hour-of-day                                  & -->
<!--   $C_3 = \lfloor z/60\rfloor\mod 24$    & -->
<!--   $P_3 = \phantom{99}24$ \\ -->
<!-- hour-of-week                                 & -->
<!--   $C_4 = \lfloor z/60\rfloor\mod 24*7$  & -->
<!--   $P_4= \phantom{9}`r 24*7`$\\ -->
<!-- day-of-week                                  & -->
<!--   $C_5 = \lfloor z/24*60\rfloor \mod 7$ & -->
<!--   $P_5= \phantom{999}7$\\ -->
<!-- \bottomrule -->
<!-- \end{tabular} -->
<!-- \end{center} -->
<!-- \caption{Examples of circular granularities with bottom granularity minutes. Circular granularity $C_i$ relates two linear granularities one of which groups periodically into the other with regular mapping and period $P_i$. Circular granularities can be expressed using modular arithmetic due to their regular mapping. } -->
<!-- \label{tab:definitions} -->
<!-- \end{table} -->

@@

<!-- \begin{table}[ht] -->
<!-- \centering -->
<!-- \begin{tabular}{lr@{~}lr@{~}r} -->
<!-- \toprule -->
<!-- Quasi-circular granularity && Possible period lengths\\ -->
<!-- \midrule -->
<!-- $Q_1 =$ day-of-month && $P_1 = 31, 30, 29, 28$\\ -->
<!-- $Q_2 =$ hour-of-month && $P_2 = 24\times 31, 24\times 30, 24\times 29, 24\times 28$\\ -->
<!-- $Q_3 =$ day-of-year && $P_3 = 366, 365$\\ -->
<!-- $Q_4 =$ week-of-month && $P_4 = 5, 4$\\ -->
<!-- \bottomrule -->
<!-- \end{tabular} -->
<!-- \caption{Examples of quasi-circular granularities relating two linear granularities with irregular mapping leading to several possible period lengths.} -->
<!-- \label{tab:quasi} -->
<!-- \end{table} -->

@@

\autoref{fig:allFig} (a) shows the distribution of half-hourly electricity consumption through letter value plots across months of the year faceted by quarters of the year. This plot does not work because quarter-of-the-year clashes with month-of-the-year, leading to empty subsets. For example, the first quarter never corresponds to December.

@@

For example, \autoref{fig:allFig} (b) shows the letter value plot across weekday/weekend faceted by quarters of the year and \autoref{fig:allFig} (c) shows the same two cyclic granularities with their mapping reversed. \autoref{fig:allFig} (b) helps us to compare weekday and weekend within each quarter and \autoref{fig:allFig} (c) helps to compare quarters within weekend and weekday.
